---
title: "R Notebook"
output: html_notebook
---

```{r}
library(here)
```

```{r}
clean_cake_data <- read_csv(here("clean_data/clean_cake_data.csv"))
```

Which cake has the most cocoa in it? 

One Bowl Chocolate. 

```{r}
clean_cake_data %>% 
  filter(ingredient == "Cocoa") %>% 
  slice_max(quantities, n = 1) 
```

For sponge cake, how many cups of ingredients are used in total? 

3.5 cups. 

#Filtered by sponge cake and cup measurement 
#Summed the total quantities where the measurement was cup 

```{r}
clean_cake_data %>% 
  filter(cake == "Sponge") %>% 
  filter(measure == "cup") %>% 
  summarise(total_cups = sum(quantities)) 
  
```

How many ingredients are measured in teaspoons? 

8 ingredients. 

```{r}
clean_cake_data %>% 
  group_by(ingredient, measure) %>% 
  distinct(ingredient) %>% 
  filter(measure == "teaspoon") 
```

Which cake has the most unique ingredients? 

Angel cake. 

#Filtered out the ingredients that had a quantity of less than zero 
#Created a new column containing the count of ingredient use 
#Filtered to find the ingredients only used once 
#Grouped by cake and made a new column containing the cakes with most unique ingredients 

```{r}
clean_cake_data %>% 
  filter(quantities > 0.00) %>%
  group_by(ingredient) %>% 
  mutate(ingredient_count = n()) %>%
  ungroup() %>%
  filter(ingredient_count == 1) %>% 
  group_by(cake) %>% 
  summarise(num_ingredients = n()) 
  
```
 
 Which ingredients are used only once? 
 
 Cream of tartar, egg white, dried currants, zwiebach, crushed ice, nuts, nutmeg and bananas. 
 
#Filtered the quantities that are less than 0 
#Created a new column with a count of the ingredient occurrences 
#Filtered to find ingredients that occurred once 
 
```{r}
clean_cake_data %>% 
  group_by(ingredient) %>% 
  filter(quantities > 0) %>% 
  mutate(ingredient_count = n()) %>% 
  filter(ingredient_count == 1) 
```

