---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse) 
library(dplyr) 
library(janitor) 
library(here) 
library(stringr) 
```

```{r}
candy_data <- read_csv(here("clean_data/clean_halloween_candy_data.CSV"))
```

```{r}
head(candy_data) 
sum(is.na(candy_data$ratings))
```

What is the total number of candy ratings given across the three years 
(Number of candy ratings, not number of raters. Don’t count missing values) 

There is no missing values in the ratings column so the total number of ratings is 542900

```{r}
candy_data %>% 
  select(ratings) %>% 
  summarise(total_ratings = n()) 
```

What was the average age of people who are going out trick or treating and the average age of people not going trick or treating? 

Not going: 39 
Going: 35 

```{r}
candy_data %>% 
  filter(age < 100) %>% 
  group_by(are_you_going_actually_going_trick_or_treating_yourself) %>% 
  summarise(mean_age_trick_treating = mean(age)) 
```

For each of joy, despair and meh, which candy bar received the most of these ratings? 

Reece's peanut butter cups recieved the most joy ratings, mary janes recieved the most despair ratings and lollipops recieved the most meh ratings. 

```{r}
candy_data %>% 
  group_by(candy, ratings)  %>% 
  summarise(count = n()) %>% 
  arrange(count)
``` 
How many people rated Starburst as despair? 
RDespair was put for Starburst 1990 times 

```{r}
candy_data %>% 
  group_by(ratings) %>% 
  filter(candy == "starburst") %>% 
  summarise(starburst_rating = n())
  
```
  
For the next three questions, count despair as -1, joy as +1 and meh as 0 

What was the most popular candy bar by this rating system for each gender in the dataset? 
#Recoding the ratings 

```{r}
mutated_data <- candy_data %>% 
  mutate(ratings = recode(ratings, "DESPAIR" = -1, "JOY" = +1, "MEH" = 0))
```

```{r}
mutated_data %>% 
  group_by(ratings, gender, candy) %>% 
  summarise(count = sum(ratings)) %>% 
  filter(gender == "Male") %>% 
  arrange(count) 
```

What was the most popular candy bar in each year? 

Reece's peanut butter cups were the most popular candy bar in 2015 and 2017. KitKat was the most popular in 2016. 

```{r}
mutated_data %>% 
  group_by(year, candy) %>% 
  summarise(count = sum(ratings)) %>% 
  arrange(count) 
```

What was the most popular candy bar by this rating for people in US, Canada, UK and all other countries? 

```{r}

```

