---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse) 
library(dplyr) 
library(janitor) 
library(here) 
library(stringr) 
```

```{r}
candy_data <- read_csv(here("clean_data/cleaned_halloween_candy_data.CSV"))
```

```{r}
head(candy_data) 
sum(is.na(candy_data$ratings))
```

What is the total number of candy ratings given across the three years 
(Number of candy ratings, not number of raters. Don’t count missing values) 

#There is no missing values in the ratings column so the total number of ratings is 542900

```{r}
candy_data %>% 
  select(ratings) %>% 
  summarise(total_ratings = n()) 
```

What was the average age of people who are going out trick or treating and the average age of people not going trick or treating? 

```{r}
candy_data %>% 
  filter(age < 100) %>% 
  group_by(are_you_going_actually_going_trick_or_treating_yourself) %>% 
  summarise(mean_age_trick_treating = mean(age)) 
```

For each of joy, despair and meh, which candy bar received the most of these ratings? 

```{r}
candy_data %>% 
  
```

